---
title: "Credit Risk Analysis"
author: "Dr. Juliho Castillo"
date: "6 de septiembre de 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Introduction and data preprocessing

## The Data

```{r}
loan_data <- readRDS("./data/loan_data_ch1.rds")
head(loan_data,10)
```
## CrossTable
```{r}
library(gmodels)
CrossTable(loan_data$home_ownership)
```

```{r}
CrossTable(loan_data$home_ownership, loan_data$loan_status, prop.r = TRUE,
           prop.c = FALSE, prop.t = FALSE, prop.chisq = FALSE)
```

### Exploring the credit data

View the structure of loan_data
```{r}
library(dplyr)
glimpse(loan_data)
```

Call CrossTable() on loan_status
```{r}
CrossTable(loan_data$loan_status)
```

Call CrossTable() on grade and loan_status
```{r}
CrossTable(loan_data$grade, loan_data$loan_status, prop.r=T, prop.c=F, prop.t=F, prop.chisq=F)
```

The proportion of defaults increases when the credit rating moves from A to G

## Histogram and outliers

using function  `hist()` 

```{r}
library(ggplot2)
ggplot(loan_data, aes(x=int_rate)) +
  geom_histogram( ) +
  ggtitle("Histogram of interest rate") +
  xlab("Interest rate")
```

Using function `hist()` on `annual_inc`

```{r}
ggplot(loan_data, aes(x=annual_inc)) +
  geom_histogram() +
  xlab("Annual Income") +
  ggtitle("Histogram of Annual Income")
```

```{r}
n_ <- sqrt(nrow(loan_data)) 
m = min(loan_data$annual_inc)
M = max(loan_data$annual_inc)
n_breaks = seq(m,M,(M-m)/(n_-1))

hist_income_n <- ggplot(loan_data, aes(x=annual_inc)) +
  geom_histogram(breaks=n_breaks ) 

hist_income_n
```

```{r}
ggplot(loan_data, aes(x=1, y=(annual_inc))) +
  geom_boxplot()
```


```{r}
ggplot(loan_data, aes(x=1, y=log(annual_inc))) +
  geom_boxplot()
```

Expert judgement vs Rule Of Thum

* “Annual salaries > $ 3 million are outliers”
```{r}
loan_data_expert <- loan_data %>%
  filter(annual_inc <= 3*10^6)

n = nrow(loan_data_expert)
l = sqrt(n)

ggplot(loan_data_expert, aes(x = annual_inc)) +
  geom_histogram(binwidth = l)
```

* Use of a rule of thumb: outlier if bigger than Q3 + 1.5 * IQR
```{r}
outlier_cutoff <- quantile(loan_data$annual_inc, 0.75) + 1.5*IQR(loan_data$annual_inc) 

loan_data_ROT <- loan_data %>%
  filter(annual_inc <= outlier_cutoff)

n = nrow(loan_data_ROT)
l = sqrt(n)


ggplot(loan_data_ROT, aes(x = annual_inc)) +
  geom_histogram(binwidth = l)
```

## Missing Data and Coarse Classifitacion

```{r}
summary(loan_data_ROT)
```

